---
output: github_document
---

```{r, echo=FALSE}
library(knitr)
opts_chunk$set(error = TRUE, cache = FALSE)
```

# thefu
Handy corrections for when you fucked up.
Inspired by [nvbn/thefuck](https://github.com/nvbn/thefuck).

## Install
```{r, eval=FALSE}
devtools::install_github("jakob-r/thefu")
```
And totally recommended:
Run in command line or edit with your favourite text editor:
```
vi ~/.Rprofile
```
Change the `.Rprofile` so that it has the following lines somewhere.
```
.First = function() {
  if (interactive()) {
    library("thefu")
  }
}
```

## Usage
```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
try(remove.packages("purrr"), silent = TRUE)
library(thefu)
```

You misspelled an installed package?

```{r}
library(e1061)
fu()
```

Thought you already have the package installed?

```{r}
library(purrr)
fu()
```

```{r, include=FALSE}
try(remove.packages("randomsearch"), silent = TRUE)
```

That package you don't know if you have it installed or how it is called exactly?

```{r}
library(randomserch)
fu(confirm = TRUE)
```
